
\documentclass[letterpaper]{article}
\usepackage[chorded]{songs}
\usepackage{geometry}
\geometry{margin=1in}
\noversenumbers

\newindex{titleidx}{titleidx}
\newauthorindex{authidx}{authidx}
\newindex{hymnidx}{hymnidx}

\begin{document}

\showindex[2]{Index by Title}{titleidx}
\showindex[2]{Index by Author}{authidx}

\songsection {Worship Songs}

\begin{songs}{titleidx,authidx}
\beginsong{Amazing Grace}[
    by = {John Newton},
    cr = {Public Domain},
    li = {(because it's old)}]
    
    \indextitleentry[hymnidx]{Amazing Grace}
    
    \beginverse
    Am\[C]azing Grace, how sw\[F]eet the s\[C]ound,
    That s\[C]aved a wretch like m\[G]e.
    I \[C]once was lost but n\[F]ow I'm f\[C]ound,
    Was bl\[Am]ind, but n\[G]ow I s\[C]ee.
    \endverse
    
    \chordsoff
    
    \beginverse
    'Twas Grace that taught,
    my heart to fear.
    And grace, my fears relieved.
    How precious did that grace appear,
    the hour I first believed.
    \endverse

    \beginverse
    Through many dangers, toils and snares,
    I have already come. 
    'Tis grace that brought me safe thus far,
    and grace will lead us home.
    \endverse

    \beginverse
    The Lord has promised good to me,
    His word my hope secures.
    He will my shield and portion be,
    as long as life endures.
    \endverse

    \beginverse
    When we've been there ten thousand years,
    bright shining as the sun.
    We've no less days to sing God's praise,
    than when we first begun.
    \endverse
\endsong

%%%%
\beginsong{Be Still My Soul}[]
    \indextitleentry[hymnidx]{Be Still My Soul}
    
    \beginverse
    Be still, my soul: the Lord is on thy side.
    Bear patiently the cross of grief or pain.
    Leave to thy God to order and provide;
    In every change, He faithful will remain.
    Be still, my soul: thy best, thy heavenly Friend
    Through thorny ways leads to a joyful end. 
    \endverse

    \beginverse
    Be still, my soul: thy God doth undertake
    To guide the future, as He has the past.
    Thy hope, thy confidence let nothing shake;
    All now mysterious shall be bright at last.
    Be still, my soul: the waves and winds still know
    \endverse
    
    \beginverse
    Be still, my soul: when dearest friends depart,
    And all is darkened in the vale of tears,
    Then shalt thou better know His love, His heart,
    Who comes to soothe thy sorrow and thy fears.
    Be still, my soul: thy Jesus can repay
    From His own fullness all He takes away. 
    \endverse
    
    \beginverse
    Be still, my soul: the hour is hastening on
    When we shall be forever with the Lord.
    When disappointment, grief and fear are gone,
    Sorrow forgot, love’s purest joys restored.
    Be still, my soul: when change and tears are past
    All safe and blessèd we shall meet at last. 
    \endverse
    
    \beginverse
    Be still, my soul: begin the song of praise
    On earth, believing, to Thy Lord on high;
    Acknowledge Him in all thy words and ways,
    So shall He view thee with a well pleased eye.
    Be still, my soul: the Sun of life divine
    Through passing clouds shall but more brightly shine. 
    \endverse
\endsong

%%%%
\beginsong{Be Thou My Vision}[]
    \indextitleentry[hymnidx]{Be Thou My Vision}
    
    \beginverse
    \[D]Be Thou my \[G]vision, oh \[D]Lord of \[A]my \[D]heart
    \[Asus4]Naught be all \[A]else to me, \[G]save that Thou \[A]art
    \[G]Thou my best thought by \[D]day or by \[G A]night
    \[D]Waking or \[G]sleeping, Thy \[Asus4 A]presence my \[D]light
    \endverse

    \chordsoff

    \beginverse
    Be Thou my wisdom and Thou my true word
    I ever with Thee and Thou with me, Lord
    Thou my great Father, I Thy true son
    Thou in me dwelling and I with Thee one
    \endverse

    \beginverse
    Be Thou my battle Shield, Sword for the fight
    Be Thou my Dignity, Thou my Delight
    Thou my soul’s Shelter, Thou my high Tower
    Raise Thou me heavenward, O Power of my power
    \endverse

    \beginverse
    Riches I heed not, nor man’s empty praise
    Thou mine Inheritance, now and always
    Thou and Thou only, first in my heart
    High King of Heaven, my Treasure Thou art 
    \endverse

    \beginverse
    High King of Heaven my victory won
    May I reach heaven's joys, oh, bright heaven's sun
    Heart of my own heart whatever befall
    Still be my vision, oh Ruler of all
    \endverse
\endsong

%%
\beginsong{Oceans \\ Where Feet May Fail}[
    by = {Joel Houston, Matt Crocker, Salomon Ligthelm - Hillsong United},
    cr = {\copyright~2012 Hillsong Music Publishing},
    li = {CCLI\# 6428767}]
    %TODO um maybe you should do the intro

    \beginverse
    \[Bm]You call me out up\[A/C#]on the w\[D]aters
    The great unkn\[A]own where feet may f\[G]ail
    \[Bm]And there I find You \[A/C#]in the \[D]mystery
    In oceans d\[A]eep
    My faith will st\[G]and   
    \endverse

    \beginchorus
    \[G]And I will \[D]call upon Your \[A]name
    \[G]And keep my \[D]eyes above the \[A]waves
    When oceans \[G]rise
    My soul will \[D]rest in Your e\[A]mbrace
    For I am \[G]Yours and \[A]You are \[Bm]mine
    \endchorus

    %Interlude pls
    \chordsoff

    \beginverse
    Your grace abounds in deepest waters
    Your sovereign hand
    Will be my guide
    Where feet may fail and fear surrounds me
    You've never failed and You won't start now 
    \endverse

    %Maybe don't include this chorus because the only word
    %change is "So" at the beginning
    \beginchorus
    So I will call upon Your name
    And keep my eyes above the waves
    When oceans rise
    My soul will rest in Your embrace
    For I am Yours and You are mine
    \endchorus

    \chordson
    
    \beginverse
    \[Bm]Spirit lead me where my tr\[G]ust is without borders
    Let me w\[A]alk upon the waters
    Wher\[Em]ever You would call me
    \[Bm]Take me deeper than my f\[G]eet could ever wander
    And my f\[D]aith will be made stronger
    In the pr\[A]esence of my Savior
    \endverse
\endsong
\end{songs}

\showindex[2]{Traditional}{hymnidx}

\end{document}

